### 2025-05-19 paper.tex
Start of Paper

%! Author = JustinMa
%! Date = 5/19/25

% Preamble
\documentclass[12pt]{article}

% Packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{caption}
\usepackage{float}

\title{Investigating Overfitting in Convolutional Neural Networks}
\date{\today}

% Document
\begin{document}

    \maketitle

    \section*{1. Introduction}

    Neural networks are a form of machine learning models, roughly inspired from how the human brain processes information.
    They have become increasingly prevalent in our developing world, providing powerful and unique solutions to a wide variety of problems.
    However, with power also comes risk, as training a neural network too much can cause overfitting.
    Overfitting occurs when a model learns the training data too well and performs poorly on unseen data.
    In this study, we investigate whether increasing the number of parameters in a convolutional neural network
    leads to greater overfitting, as measured by the difference between training and test accuracy.

    \section*{2. Statistical Question}

    Does increasing the number of parameters in a fixed CNN architecture cause a greater difference between training and testing accuracy?

    \subsection*{Hypotheses}

    $H_0: \beta = 0$ \newline
    $H_a: \beta \geq 0$
    \newline \newline
    Where $\beta$ is the true slope of the population least-squares regression line that relates number of parameters of the model to the difference in accuracy of the model on the train dataset and the test dataset.

    \section*{3. Data Collection}

    We trained \mathbf{x} convolutional models on the CIFAR-10 dataset, each with the same architecture (pictured below) but different numbers of
    parameters ranging from approximately 1 million to 50 million.

    For each model, we calculated:

    \[
        \Delta \text{Accuracy} = \text{Train Accuracy} - \text{Test Accuracy}
    \]

    We then analyzed the relationship between \( \Delta \text{Accuracy} \) and the model size.

    \section*{Data Display}

    \section*{Data Analysis}

    \section*{Conclusion}

    \section*{Reflection}
\end{document}

### 2025-05-19 paper.tex
Got rid of chatgpt writing
fixed crash with \mathbf

@@
 
-    We trained \mathbf{x} convolutional models on the CIFAR-10 dataset, each with the same architecture (pictured below) but different numbers of
+    We trained $\mathbf{x}$ convolutional models on the CIFAR-10 dataset, each with the same architecture (pictured below) but different numbers of
     parameters ranging from approximately 1 million to 50 million.
-
-    For each model, we calculated:
-
-    \[
-        \Delta \text{Accuracy} = \text{Train Accuracy} - \text{Test Accuracy}
-    \]
-
-    We then analyzed the relationship between \( \Delta \text{Accuracy} \) and the model size.
 

### 2025-05-19 paper.tex
added some stuff

@@
 \usepackage{float}
+\usepackage{tikz}
+\usepackage{setspace}
 
-\title{Investigating Overfitting in Convolutional Neural Networks}
-\date{\today}
+\doublespacing
+\usetikzlibrary{shapes.geometric, arrows.meta, positioning}
+
+\tikzstyle{layer} = [rectangle, draw=black, minimum width=5cm, minimum height=1cm, text centered, text width=5cm]
+\tikzstyle{arrow} = [thick, -{Stealth}]
 
 % Document
+\usepackage{times}
 \begin{document}
 
-    \maketitle
+    \centerline{\textbf{Investigating Overfitting in Convolutional Neural Networks}}
 
-    \section*{1. Introduction}
+    \noindent\textbf{1. Introduction}
 
@@
 
-    \section*{2. Statistical Question}
+    \noindent\textbf{2. Statistical Question}
 
@@
 
-    \subsection*{Hypotheses}
-
+    \noindent\textbf{Hypotheses}\newline
     $H_0: \beta = 0$ \newline
@@
 
-    \section*{3. Data Collection}
+    \noindent\textbf{3. Data Collection}
 
-    We trained $\mathbf{x}$ convolutional models on the CIFAR-10 dataset, each with the same architecture (pictured below) but different numbers of
-    parameters ranging from approximately 1 million to 50 million.
+    We trained $\mathbf{x}$ convolutional models on a randomly selected small subset of size 100 images from the CIFAR-10 dataset, each with the same architecture (\textit{see figure 1}).
+    Each model had a different number of parameters, uniformly ranging from approximately 1 million to 50 million.
 
-    \section*{Data Display}
+    % Model Architecture
+    \noindent\textbf{Model Architecture}
+    \begin{center}
+        \begin{tikzpicture}[node distance=1.2cm]
 
-    \section*{Data Analysis}
+            \node (input) [layer, fill=gray!10] {Input: (32, 32, 3)};
+            \node (conv1) [layer, fill=blue!10, below of=input] {Conv2D: filters=$32\cdot k$, kernel=3×3, activation=ReLU};
+            \node (pool1) [layer, fill=cyan!10, below of=conv1] {MaxPooling2D: pool=2×2};
+            \node (conv2) [layer, fill=blue!10, below of=pool1] {Conv2D: filters=$64\cdot k$, kernel=3×3, activation=ReLU};
+            \node (pool2) [layer, fill=cyan!10, below of=conv2] {MaxPooling2D: pool=2×2};
+            \node (flatten) [layer, fill=orange!10, below of=pool2] {Flatten};
+            \node (dense1) [layer, fill=green!15, below of=flatten] {Dense: layer size=$128\cdot k$, activation=ReLU};
+            \node (dense2) [layer, fill=green!15, below of=dense1] {Dense: layer size=$64\cdot k$, activation=ReLU};
+            \node (output) [layer, fill=red!15, below of=dense2] {Dense (Output): 10 units, activation=Softmax};
 
-    \section*{Conclusion}
+            \draw [arrow] (input) -- (conv1);
+            \draw [arrow] (conv1) -- (pool1);
+            \draw [arrow] (pool1) -- (conv2);
+            \draw [arrow] (conv2) -- (pool2);
+            \draw [arrow] (pool2) -- (flatten);
+            \draw [arrow] (flatten) -- (dense1);
+            \draw [arrow] (dense1) -- (dense2);
+            \draw [arrow] (dense2) -- (output);
 
-    \section*{Reflection}
+        \end{tikzpicture}
+    \end{center}
+
+    \centerline{\textit{Figure 1: Architecture of CNN Model}}
+
+    \noindent\textbf{Data Display}
+
+    \noindent\textbf{Data Analysis}
+
+    \noindent\textbf{Conclusion}
+
+    \noindent\textbf{Reflection}
 \end{document}

### 2025-05-19 paper.tex
Made diagram look better and added a sentence about randomization to Data Collection section. I also revised the introduction slightly, still needs work.

--- 2025-05-19 paper.tex
@@
-%! Author = JustinMa
-%! Date = 5/19/25
+% !Author = JustinMa
+% !Date = 5/19/25
 
-% Preamble
 \documentclass[12pt]{article}
@@
 \usepackage{float}
+\usepackage{tikz}
+\usepackage{setspace}
+\usepackage{times}
 
-\title{Investigating Overfitting in Convolutional Neural Networks}
-\date{\today}
+\doublespacing
 
-% Document
+% TikZ libraries and styles
+\usetikzlibrary{shapes.geometric, arrows.meta, positioning, shadows}
+
+\tikzset{
+    layer/.style={
+        rectangle,
+        draw=black!80,
+        rounded corners,
+        minimum width=5cm,
+        minimum height=0.6cm,
+        text centered,
+        text width=7cm,
+        font=\small,
+        drop shadow,
+        fill=#1
+    },
+    arrow/.style={
+        -{Stealth[length=2mm]},
+        thick,
+        shorten >=2pt,
+        shorten <=2pt
+    }
+}
+
 \begin{document}
 
-    \maketitle
+    \centerline{\textbf{Investigating Overfitting in Convolutional Neural Networks}}
 
-    \section*{1. Introduction}
+    \noindent\textbf{1. Introduction}
 
-    Neural networks are a form of machine learning models, roughly inspired from how the human brain processes information.
-    They have become increasingly prevalent in our developing world, providing powerful and unique solutions to a wide variety of problems.
-    However, with power also comes risk, as training a neural network too much can cause overfitting.
-    Overfitting occurs when a model learns the training data too well and performs poorly on unseen data.
-    In this study, we investigate whether increasing the number of parameters in a convolutional neural network
-    leads to greater overfitting, as measured by the difference between training and test accuracy.
+    Neural networks are a form of machine learning models, roughly inspired by how the human brain
+    processes information. They have become increasingly prevalent in our developing world, providing
+    powerful and unique solutions to a wide variety of problems. However, with power also comes risk,
+    as training a neural network too much on a small dataset can cause overfitting. Overfitting occurs
+    when a model learns the training data too well by essentially memorizing it, causing it to perform
+    well on data in its training set but poorly on unseen data. While it might seem that simply
+    increasing a model’s size would always boost accuracy by allowing it to capture more patterns,
+    extra parameters often give the network enough capacity to store the training set outright, allowing
+    it to overfit. Smaller networks, by contrast, are forced to find the underlying patterns in the data
+    because of their limited size. In this study, we investigate whether increasing the number of parameters
+    in a convolutional neural network leads to greater overfitting when trained on a small dataset, as
+    measured by the difference between training and test accuracy.
 
-    \section*{2. Statistical Question}
+    \noindent\textbf{2. Statistical Question}
 
-    Does increasing the number of parameters in a fixed CNN architecture cause a greater difference between training and testing accuracy?
+    Does increasing the number of parameters in a fixed CNN architecture cause a greater difference
+    between training and testing accuracy?
 
-    \subsection*{Hypotheses}
+    \noindent\textbf{Hypotheses}\newline
+    $H_0: \beta = 0$ \newline
+    $H_a: \beta > 0$ \newline\newline
+    Where $\beta$ is the true slope of the population least‐squares regression line that relates number
+    of parameters of the model to the difference in accuracy of the model on the train dataset and the
+    test dataset.
 
-    $H_0: \beta = 0$ \newline
-    $H_a: \beta \geq 0$
-    \newline \newline
-    Where $\beta$ is the true slope of the population least-squares regression line that relates number of parameters of the model to the difference in accuracy of the model on the train dataset and the test dataset.
+    \noindent\textbf{3. Data Collection}
 
-    \section*{3. Data Collection}
+    We trained $\mathbf{x}$ convolutional models on a randomly selected small subset of size 100 images
+    from the CIFAR-10 dataset, each with the same architecture (\textit{see figure 1}). Each model had
+    a different number of parameters, roughly uniformly ranging from approximately 1 million to 50 million.
+    For each model, the initial values of the parameters are randomly set, so each model can be seen as randomly
+    selected from all possible models of that size and architecture before training.
 
-    We trained $\mathbf{x}$ convolutional models on the CIFAR-10 dataset, each with the same architecture (pictured below) but different numbers of
-    parameters ranging from approximately 1 million to 50 million.
+    \noindent\textbf{Model Architecture}
+    \begin{center}
+        \begin{tikzpicture}[node distance=4mm and 0mm]
+            \node[layer=gray!10]                     (input)  {Input $(32\times32\times3)$};
+            \node[layer=blue!10,  below=of input]    (conv1)  {Conv2D: $32n$ filters, $3\times3$, ReLU};
+            \node[layer=cyan!10,  below=of conv1]    (pool1)  {MaxPool: $2\times2$};
+            \node[layer=blue!10,  below=of pool1]    (conv2)  {Conv2D: $64n$ filters, $3\times3$, ReLU};
+            \node[layer=cyan!10,  below=of conv2]    (pool2)  {MaxPool: $2\times2$};
+            \node[layer=orange!10,below=of pool2]    (flat)   {Flatten};
+            \node[layer=green!15, below=of flat]    (dense1) {Dense: $128n$, ReLU};
+            \node[layer=green!15, below=of dense1]  (dense2) {Dense: $64n$, ReLU};
+            \node[layer=red!15,   below=of dense2]  (output) {Dense (Output): 10, Softmax};
 
-    \section*{Data Display}
+            \draw[arrow] (input)  -- (conv1);
+            \draw[arrow] (conv1)  -- (pool1);
+            \draw[arrow] (pool1)  -- (conv2);
+            \draw[arrow] (conv2)  -- (pool2);
+            \draw[arrow] (pool2)  -- (flat);
+            \draw[arrow] (flat)   -- (dense1);
+            \draw[arrow] (dense1) -- (dense2);
+            \draw[arrow] (dense2) -- (output);
+        \end{tikzpicture}
+    \end{center}
 
-    \section*{Data Analysis}
+    \centerline{\textit{Figure 1: Architecture of CNN Model}}
 
-    \section*{Conclusion}
+    \noindent\textbf{Data Display}
 
-    \section*{Reflection}
+    \noindent\textbf{Data Analysis}
+
+    \noindent\textbf{Conclusion}
+
+    \noindent\textbf{Reflection}
+
 \end{document}

### 2025-05-20 paper.tex
fixed margins

@@
 \usepackage{times}
+\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
 
@@
 
-    \noindent\textbf{Hypotheses}\newline
-    $H_0: \beta = 0$ \newline
-    $H_a: \beta > 0$ \newline\newline
+    \noindent\textbf{Hypotheses:}\newline
+    \centerline{$H_0: \beta = 0$} \newline
+    \centerline{$H_a: \beta > 0$} \newline
     Where $\beta$ is the true slope of the population least‐squares regression line that relates number
@@
     a different number of parameters, roughly uniformly ranging from approximately 1 million to 50 million.
+    We controlled the parameter count by multiplying the amount of filters for the Conv2D layers and the amount of units
+    for the hidden Dense layers by a scalar factor, $n$.
     For each model, the initial values of the parameters are randomly set, so each model can be seen as randomly
@@
             \node[layer=orange!10,below=of pool2]    (flat)   {Flatten};
-            \node[layer=green!15, below=of flat]    (dense1) {Dense: $128n$, ReLU};
-            \node[layer=green!15, below=of dense1]  (dense2) {Dense: $64n$, ReLU};
+            \node[layer=green!15, below=of flat]    (dense1) {Dense: $128n$ units, ReLU};
+            \node[layer=green!15, below=of dense1]  (dense2) {Dense: $64n$ units, ReLU};
             \node[layer=red!15,   below=of dense2]  (output) {Dense (Output): 10, Softmax};
@@
 
-    \centerline{\textit{Figure 1: Architecture of CNN Model}}
+    \centerline{\textit{Figure 1: General Architecture of Our Models}}
 

### 2025-05-20 paper.tex
Added content to the data collection section.

@@
     of parameters of the model to the difference in accuracy of the model on the train dataset and the
-    test dataset.
+    test dataset (train - test).
 
@@
 
-    We trained $\mathbf{x}$ convolutional models on a randomly selected small subset of size 100 images
-    from the CIFAR-10 dataset, each with the same architecture (\textit{see figure 1}). Each model had
-    a different number of parameters, roughly uniformly ranging from approximately 1 million to 50 million.
-    We controlled the parameter count by multiplying the amount of filters for the Conv2D layers and the amount of units
+    We trained $15$ sets containing $3$ convolutional models each on a randomly selected small subset of size 100 images
+    from the CIFAR-10 dataset, each model having the same architecture (\textit{see figure 1 below}).
+    Models within a set had the same number of parameters, and separate sets had different numbers of parameters,
+    uniformly ranging from approximately 1 million to 50 million.
+    On the initialization of each model in each set, the values of the parameters are randomly set, so each model can be seen as randomly
+    selected from all possible models of their respective size and architecture before training.
+    We controlled the parameter count by multiplying the amount of filters for the Conv2D layers and the amount of neurons
     for the hidden Dense layers by a scalar factor, $n$.
-    For each model, the initial values of the parameters are randomly set, so each model can be seen as randomly
-    selected from all possible models of that size and architecture before training.
 
@@
             \node[layer=gray!10]                     (input)  {Input $(32\times32\times3)$};
-            \node[layer=blue!10,  below=of input]    (conv1)  {Conv2D: $32n$ filters, $3\times3$, ReLU};
+            \node[layer=blue!10,  below=of input]    (conv1)  {Conv2D: $32\cdot n$ filters, $3\times3$, ReLU};
             \node[layer=cyan!10,  below=of conv1]    (pool1)  {MaxPool: $2\times2$};
-            \node[layer=blue!10,  below=of pool1]    (conv2)  {Conv2D: $64n$ filters, $3\times3$, ReLU};
+            \node[layer=blue!10,  below=of pool1]    (conv2)  {Conv2D: $64\cdot n$ filters, $3\times3$, ReLU};
             \node[layer=cyan!10,  below=of conv2]    (pool2)  {MaxPool: $2\times2$};
             \node[layer=orange!10,below=of pool2]    (flat)   {Flatten};
-            \node[layer=green!15, below=of flat]    (dense1) {Dense: $128n$ units, ReLU};
-            \node[layer=green!15, below=of dense1]  (dense2) {Dense: $64n$ units, ReLU};
+            \node[layer=green!15, below=of flat]    (dense1) {Dense: $128\cdot n$ units, ReLU};
+            \node[layer=green!15, below=of dense1]  (dense2) {Dense: $64\cdot n$ units, ReLU};
             \node[layer=red!15,   below=of dense2]  (output) {Dense (Output): 10, Softmax};
@@
 
+    For each set, each model was trained for $60$ epochs on the randomly selected subset of 100 images and then tested
+    on the full test set of CIFAR-10. The difference between the train and test accuracy (train - test) was then
+    computed for each model, and the average of that value was computed for each set of models by adding up all of
+    the differences and then dividing by the size of the set. Then, the data were graphed on a scatter plot with the x-axis
+    as parameter number and the y-axis as the calculated average difference between train and test accuracy for each set of models.
+
     \noindent\textbf{Data Display}

### 2025-05-21 paper.tex
Added more information to all sections. Sentence structure/grammar and conciseness might need some work though.

@@
     when a model learns the training data too well by essentially memorizing it, causing it to perform
-    well on data in its training set but poorly on unseen data. While it might seem that simply
-    increasing a model’s size would always boost accuracy by allowing it to capture more patterns,
-    extra parameters often give the network enough capacity to store the training set outright, allowing
-    it to overfit. Smaller networks, by contrast, are forced to find the underlying patterns in the data
-    because of their limited size. In this study, we investigate whether increasing the number of parameters
-    in a convolutional neural network leads to greater overfitting when trained on a small dataset, as
-    measured by the difference between training and test accuracy.
+    well on data in its training set but poorly on test data (data that were not in the training set).
+    While it might seem that simply increasing a model’s size would always boost accuracy by allowing it to
+    capture more patterns, extra parameters often give the network enough capacity to store the training set
+    outright when the training set is small, allowing it to overfit. Smaller networks, by contrast, are forced to find the underlying patterns
+    in the data because of their limited size. In this study, we investigate whether increasing the number of
+    parameters in a convolutional neural network leads to greater overfitting when trained on a small dataset, as
+    measured by the difference between its accuracy on the training dataset and the test dataset.
 
@@
 
-    We trained $15$ sets containing $3$ convolutional models each on a randomly selected small subset of size 100 images
-    from the CIFAR-10 dataset, each model having the same architecture (\textit{see figure 1 below}).
-    Models within a set had the same number of parameters, and separate sets had different numbers of parameters,
-    uniformly ranging from approximately 1 million to 50 million.
+    We trained $100$ convolutional models each on the same randomly selected small subset of 100 images
+    from the Canadian Institute For Advanced Research - 10 dataset (CIFAR-10), which consists of 32x32 color images labeled with one one of ten classes (e.g., plane, boat, etc).
+    Each model had the same architecture, the only difference between them being the number of parameters (\textit{see figure 1 below}).
+    The training dataset was constructed by randomly selecting 10 of each class of image to ensure that it is representative of the entire dataset.
+    The number of filters and neurons in each model were varied so that the model sizes are roughly uniform, ranging from approximately 1m - 50m parameters.
+    The architecture and the ratio of layer sizes were also kept the same for each model, making sure the only difference between them is the number of parameters.
     On the initialization of each model in each set, the values of the parameters are randomly set, so each model can be seen as randomly
-    selected from all possible models of their respective size and architecture before training.
+    selected from all possible models of their respective size and architecture before training, ensuring the experiment is statistically valid.
     We controlled the parameter count by multiplying the amount of filters for the Conv2D layers and the amount of neurons
@@
             \node[layer=orange!10,below=of pool2]    (flat)   {Flatten};
-            \node[layer=green!15, below=of flat]    (dense1) {Dense: $128\cdot n$ units, ReLU};
-            \node[layer=green!15, below=of dense1]  (dense2) {Dense: $64\cdot n$ units, ReLU};
+            \node[layer=green!15, below=of flat]    (dense1) {Dense: $128\cdot n$ neurons, ReLU};
+            \node[layer=green!15, below=of dense1]  (dense2) {Dense: $64\cdot n$ neurons, ReLU};
             \node[layer=red!15,   below=of dense2]  (output) {Dense (Output): 10, Softmax};
@@
 
-    For each set, each model was trained for $60$ epochs on the randomly selected subset of 100 images and then tested
-    on the full test set of CIFAR-10. The difference between the train and test accuracy (train - test) was then
-    computed for each model, and the average of that value was computed for each set of models by adding up all of
-    the differences and then dividing by the size of the set. Then, the data were graphed on a scatter plot with the x-axis
-    as parameter number and the y-axis as the calculated average difference between train and test accuracy for each set of models.
+    Each model was trained for $100$ epochs on the randomly selected subset of 100 images and then tested
+    on the full test set of the CIFAR-10 dataset, made up of $10,000$ images. The difference between the train and test accuracy (train - test) was then
+    computed for each model and graphed on a scatter plot with the x-axis
+    as parameter count and the y-axis as the difference between train and test accuracy for each model.
 

### 2025-05-22 paper_formatted.tex
added a formatted version of the paper for better aesthetics, the formatting still needs to be slightly fixed on the nonformatted one (the one to submit)

--- 2025-05-21 paper.tex
@@
-% !Author = JustinMa
-% !Date = 5/19/25
+%! Author = JustinMa
+%! Date = 5/22/25
 
@@
 
+\title{Investigating Overfitting in Convolutional Neural Networks}\date{}
+
 \begin{document}
 
-    \centerline{\textbf{Investigating Overfitting in Convolutional Neural Networks}}
+    \maketitle
 
-    \noindent\textbf{1. Introduction}
+    \section*{1. Introduction}
 
@@
 
-    \noindent\textbf{2. Statistical Question}
+    \section*{2. Statistical Question}
 
@@
 
-    \noindent\textbf{3. Data Collection}
+    \section*{3. Data Collection}
 
@@
 
-    \noindent\textbf{Data Display}
+    \section*{4. Data Display}
 
-    \noindent\textbf{Data Analysis}
+    \section*{5. Data Analysis}
 
-    \noindent\textbf{Conclusion}
+    We conducted a $t$-test for the population slope $\beta$ of the least-squares regression line that relates the number of parameters in a model trained on a 100-image subset of the CIFAR-10 dataset to the difference in accuracy between training and test data (Train Accuracy $-$ Test Accuracy).
 
-    \noindent\textbf{Reflection}
+    \subsection*{5.1 Condition Check}
+
+    \begin{quote}
+
+    \textbf{5.1.1 Linear}
+
+    {The scatterplot of the data shows a clear linear trend, and the residual plot shows no remaining curved pattern. Therefore, the linearity condition is satisfied.}
+
+    \textbf{5.1.2 Independent}
+
+    Each model was trained independently with no interaction between runs. Thus, the independence condition is met by the design of the experiment.
+
+    \textbf{5.1.3 Normal}
+    The dotplot of the residuals shows no strong skew and no outliers, suggesting the residuals are approximately normally distributed.
+
+    \textbf{5.1.4 Equal Variance}
+    The residual plot shows shows no noticeable $<$ or $>$ shape, so the equal variance condition is satisfied.
+
+    \textbf{5.1.5 Random}
+    The parameters of the model were randomized on initialization, so each model can be seen as randomly selected from the population
+    of models of the same size and structure.
+
+    \end{quote}
+
+    \subsection*{5.2 Calculations}
+
+    \section*{6. Conclusion}
+
+    \section*{7. Reflection}
 

### 2025-05-23 paper_formatted.tex
added figures/ graphs, and started calculations section.

@@
 \usepackage{booktabs}
-\usepackage{caption}
+\usepackage[labelfont=it, textfont=it]{caption}
 \usepackage{float}
@@
 \usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
+\usepackage[colorlinks=true, linkcolor=blue, citecolor=blue, urlcolor=blue]{hyperref}
 
@@
     from the Canadian Institute For Advanced Research - 10 dataset (CIFAR-10), which consists of 32x32 color images labeled with one one of ten classes (e.g., plane, boat, etc).
-    Each model had the same architecture, the only difference between them being the number of parameters (\textit{see figure 1 below}).
+    Each model had the same architecture, the only difference between them being the number of parameters (\textit{see Figure 1 below}).
     The training dataset was constructed by randomly selecting 10 of each class of image to ensure that it is representative of the entire dataset.
@@
     \noindent\textbf{Model Architecture}
+    \begin{figure}[H]
         \begin{center}
@@
             \end{tikzpicture}
+            \caption{General Architecture of Our Models}
         \end{center}
-
-    \centerline{\textit{Figure 1: General Architecture of Our Models}}
+        \label{fig:architecture}
+    \end{figure}
 
@@
     \section*{4. Data Display}
+
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=0.7\textwidth]{Images/Scatter}
+        \caption{Scatterplot of Parameter Count vs. Difference in Train and Test Accuracy (Train - Test)}
+        \label{fig:scatterplot}
+    \end{figure}
+
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=0.7\textwidth]{Images/Resid}
+        \caption{Residual Plot (Parameter Count vs. Residuals)}
+        \label{fig:residuals}
+    \end{figure}
+
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=0.7\textwidth]{Images/Resid Hist}
+        \caption{Histogram of Residuals}
+        \label{fig:residual_hist}
+    \end{figure}
 
@@
 
-    {The scatterplot of the data shows a clear linear trend, and the residual plot shows no remaining curved pattern. Therefore, the linearity condition is satisfied.}
+    The scatterplot of the data (\textit{\autoref{fig:scatterplot}}) shows a clear linear trend, and the residual plot (\textit{\autoref{fig:residuals}}) shows no remaining curved pattern.
+    Therefore, the linearity condition is satisfied.
 
@@
     \textbf{5.1.3 Normal}
-    The dotplot of the residuals shows no strong skew and no outliers, suggesting the residuals are approximately normally distributed.
+
+    The histogram of the residuals (\textit{\autoref{fig:residual_hist}}) shows no strong skew and no obvious outliers,
+    so the normality condition is met.
 
     \textbf{5.1.4 Equal Variance}
-    The residual plot shows shows no noticeable $<$ or $>$ shape, so the equal variance condition is satisfied.
+
+    The residual plot (\textit{\autoref{fig:residuals}}) shows shows no noticeable $<$ or $>$ shape, so the equal variance condition is satisfied.
 
     \textbf{5.1.5 Random}
+
     The parameters of the model were randomized on initialization, so each model can be seen as randomly selected from the population
@@
 
+    We used the following equation to calculate the Standard Error $SE_\beta$ of the slope \beta:
+
+    \begin{equation*}
+        \centering
+        SE_\beta = \frac{s}{s_x\sqrt{n - 1}}
+    \end{equation*}
+
     \section*{6. Conclusion}

### 2025-05-23 paper_formatted.tex
Added to calculations

@@
 
-    We trained $100$ convolutional models each on the same randomly selected small subset of 100 images
+    We trained $150$ convolutional models each on the same randomly selected small subset of 100 images
     from the Canadian Institute For Advanced Research - 10 dataset (CIFAR-10), which consists of 32x32 color images labeled with one one of ten classes (e.g., plane, boat, etc).
@@
     The training dataset was constructed by randomly selecting 10 of each class of image to ensure that it is representative of the entire dataset.
-    The number of filters and neurons in each model were varied so that the model sizes are roughly uniform, ranging from approximately 1m - 50m parameters.
+    The number of filters and neurons in each model were varied so that the model sizes are roughly uniform, ranging from approximately 1m - 25m parameters.
     The architecture and the ratio of layer sizes were also kept the same for each model, making sure the only difference between them is the number of parameters.
@@
 
-    We used the following equation to calculate the Standard Error $SE_\beta$ of the slope \beta:
-
-    \begin{equation*}
-        \centering
-        SE_\beta = \frac{s}{s_x\sqrt{n - 1}}
-    \end{equation*}
+    We used the following equation to calculate the Standard Error $SE_\beta$ of the slope $\beta$:
+    \[
+        \mathrm{SE}_{\beta}
+        =
+        \frac{
+            \displaystyle S
+        }{
+            \displaystyle S_x \sqrt{n - 1}
+        }
+    \]
+    \noindent We need the standard deviation of the residuals and of the parameter counts to find $SE_\beta$, which we found like this:
+    \begin{align*}
+        \mathrm{S} &=
+        \sqrt{
+            \frac{
+                \sum_{i=1}^n (y_i - \hat{y}_i)^2
+            }{
+                n - 2
+            }
+        } \\[1em]
+        \mathrm{S}_x &=
+        \sqrt{
+            \frac{
+                \sum_{i=1}^n (x_i - \bar{x})^2
+            }{
+                n - 1
+            }
+        }
+    \end{align*}
+    \noindent After plugging in all of the data from the 150 models, we got $S = 0.01703$ and $S_x = 0.6972$.
+    Now we can use those to find $SE_\beta$:
+    \[
+        \mathrm{SE}_{\beta}
+        =
+        \frac{
+            \displaystyle 0.01703
+        }{
+            \displaystyle 0.6972 \sqrt{150 - 1}
+        }
+        =
+        0.002008
+    \]
+    \noindent And now we can find the t-statistic:
+    \begin{gather*}
+        \mathrm{t} = \frac{b}{SE_\beta} \\[1em]
+        \mathrm{t} = \frac{0.008312}{0.002008} = 4.139
+    \end{gather*}
 

### 2025-05-23 paper_formatted.tex
added p-value calculation and rough conclusion paragraph.

@@
 
+    \subsubsection*{5.2.1 Standard Error}
+
     We used the following equation to calculate the Standard Error $SE_\beta$ of the slope $\beta$:
@@
     \]
-    \noindent And now we can find the t-statistic:
+
+    \subsubsection*{5.2.2 $t$-statistic}
+    \noindent And now we can find the t-statistic, which represents how many standard deviations away our sample slope $b$ is from the population slope $\beta$, assuming that $\beta=0$:
     \begin{gather*}
@@
 
+    \subsubsection*{5.2.3 $p$-value}
+    \noindent Now that we have the t-statistic, we can use it to find the $p$-value, which represents the probability of getting a test statistic
+    of $4.139$ or higher, assuming that the population slope $\beta$ is $0$. Because we have 150 data points, we have $150 - 2 = 148$ degrees of freedom.
+    Thus, we calculate the $p$-value by finding the amount of area under a $t$-distribution with 148 degrees of freedom, above $t=4.139$. The graph below demonstrates this:
+
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=0.7\textwidth]{Images/tdistribution}
+        \caption{p-value calculation on a t-distribution with df = 148}
+        \label{fig:t_dist}
+    \end{figure}
+
+    \noindent Based on the area under the curve in \textit{\autoref{fig:t_dist}} above $t=4.139$, our $p$-value is $2.916\cdot10^{-5}$.
+
     \section*{6. Conclusion}
+
+    The $p$-value of $2.916\cdot10^{-5}$ indicates that, assuming that the population slope $\beta=0$, there is around a
+    $0.002916\%$ probability of getting a sample slope as great or greater than our sample slope of $0.008312$, in a sample of
+    150 randomly selected models from the population of convolutional models of our structure and of size 1 million parameters to 25 million parameters, trained
+    on a randomly selected subset of 100 images from the CIFAR-10 train dataset and tested on the full test dataset of CIFAR-10.
+    Because the $p$-value of $2.916\cdot10^{-5}$ is less than $\alpha=0.05$, we reject the null hypothesis, which states that the population slope $\beta$
+    of the least-squares regression line that relates parameter count to difference in train and test accuracy (train - test) is $0$,
+    in the population defined above.
+    The data do provide convincing evidence that the population slope $\beta$ is greater than $0$, and that there is a positive correlation between
+    parameter count and difference between train and test accuracy (train - test) in the population defined above.
 

### 2025-05-26 paper_formatted.tex
slightly fixed up data collection section and added a few descriptions to the data display section for scatterplot and resid histogram (need to be changed and polished still. Still need to possibly add summary statistics to the data display section, add reflection section, and fix up grammar/wording and polish formatting.

@@
 
-    We trained $150$ convolutional models each on the same randomly selected small subset of 100 images
-    from the Canadian Institute For Advanced Research - 10 dataset (CIFAR-10), which consists of 32x32 color images labeled with one one of ten classes (e.g., plane, boat, etc).
-    Each model had the same architecture, the only difference between them being the number of parameters (\textit{see Figure 1 below}).
-    The training dataset was constructed by randomly selecting 10 of each class of image to ensure that it is representative of the entire dataset.
-    The number of filters and neurons in each model were varied so that the model sizes are roughly uniform, ranging from approximately 1m - 25m parameters.
-    The architecture and the ratio of layer sizes were also kept the same for each model, making sure the only difference between them is the number of parameters.
-    On the initialization of each model in each set, the values of the parameters are randomly set, so each model can be seen as randomly
+    We trained 150 convolutional models, each on the same randomly selected small subset of 100 images
+    from the Canadian Institute For Advanced Research - 10 dataset (CIFAR-10), which consists of 32x32 color images each labeled with one of ten classes (e.g., plane, boat, etc).
+    % Each model had the same architecture, with the only difference between them being the number of parameters (\textit{see Figure 1 below}).
+    The training dataset was constructed through stratified random sampling by randomly selecting 10 of each class of image, ensuring that it is representative of the entire dataset.
+    The number of filters and neurons were varied between models in a way such that the sizes of the models (in parameter count) were roughly uniformly distributed, ranging from approximately 1m to 25m parameters.
+    The architecture and the ratio of layer sizes were kept consistent between each model, ensuring that the only difference between them was the number of parameters (\textit{see Figure 1 below}).
+    On the initialization of each model, the values of the parameters for that model were randomly set, so each model can be seen as randomly
     selected from all possible models of their respective size and architecture before training, ensuring the experiment is statistically valid.
@@
 
-    \noindent\textbf{Model Architecture}
     \begin{figure}[H]
@@
 
-    Each model was trained for $100$ epochs on the randomly selected subset of 100 images and then tested
-    on the full test set of the CIFAR-10 dataset, made up of $10,000$ images. The difference between the train and test accuracy (train - test) was then
+    \noindent Each model was trained for 100 epochs on the randomly selected subset of 100 images, then evaluated
+    on the full test set of the CIFAR-10 dataset, made up of 10,000 images. The difference between the train and test accuracy (train - test) was then
     computed for each model and graphed on a scatter plot with the x-axis
@@
     \section*{4. Data Display}
-
     \begin{figure}[H]
@@
     \end{figure}
-
+    There appears to be a moderate, positive, linear relationship between parameter count and difference between
+    train and test accuracy (train - test). There appear to be a few possible high outliers above $x =$ 1.5 million parameters
+    and a few possible low outliers above $x = 0.5$ million parameters.
     \begin{figure}[H]
@@
     \end{figure}
-
     \begin{figure}[H]
@@
     \end{figure}
+    \noindent The histogram of the residuals appears to be approximately symmetric, with a median around 0 and a range of
+    $0.05-(-0.04)=0.09$. There do not appear to be any obvious outliers.
 

### 2025-05-27 paper_formatted.tex
first draft for final paper; wrote reflection and changed formatting; fixed explanations and added on to some other sections.

@@
 \usepackage{times}
-\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
+\usepackage{longtable}
+\usepackage{siunitx}
+\usepackage[margin=1in]{geometry}
 \usepackage[colorlinks=true, linkcolor=blue, citecolor=blue, urlcolor=blue]{hyperref}
@@
     selected from all possible models of their respective size and architecture before training, ensuring the experiment is statistically valid.
+    All of the above precautions aimed to eliminate confounding with other variables, ensuring that any change in the accuracy of the models was actually caused by the change in parameter count.
     We controlled the parameter count by multiplying the amount of filters for the Conv2D layers and the amount of neurons
@@
         \centering
-        \includegraphics[width=0.7\textwidth]{Images/Scatter}
+        \includegraphics[width=1\textwidth]{Images/Scatter}
         \caption{Scatterplot of Parameter Count vs. Difference in Train and Test Accuracy (Train - Test)}
@@
     \end{figure}
-    There appears to be a moderate, positive, linear relationship between parameter count and difference between
-    train and test accuracy (train - test). There appear to be a few possible high outliers above $x =$ 1.5 million parameters
+
+    \begin{table}[ht]
+        \centering
+        \begin{tabular}{|l|r|r|}
+            \hline
+            Predictor & Coef & SE Coef \\
+            \hline
+            Constant & 0.7454 &  \\
+            Param Count (x10 mil)   & 0.0083 & 0.0020 \\
+            \hline
+            \multicolumn{2}{|l|}{$S = 0.01703$} & R-Sq = 10.37\% \\
+            \hline
+        \end{tabular}
+        \caption{Regression Summary}
+        \label{tab:minitab}
+    \end{table}
+
+    \noindent
+    Based on the scatter plot (\textit{\autoref{fig:scatterplot}}) and the correlation coefficient of $r=\sqrt{0.1037}=0.3220$ (\textit{from \autoref{tab:minitab}}), there appears to be a weak,
+    positive, linear relationship between parameter count and difference between train and test accuracy (train - test).
+    There appear to be a few possible high outliers above $x =$ 1.5 million parameters
     and a few possible low outliers above $x = 0.5$ million parameters.
@@
     \noindent The histogram of the residuals appears to be approximately symmetric, with a median around 0 and a range of
-    $0.05-(-0.04)=0.09$. There do not appear to be any obvious outliers.
+    $0.05-(-0.04)=0.09$. There does not appear to be any strong skew or outliers.
 
@@
     \subsubsection*{5.2.2 $t$-statistic}
-    \noindent And now we can find the t-statistic, which represents how many standard deviations away our sample slope $b$ is from the population slope $\beta$, assuming that $\beta=0$:
+    \noindent And now we can find the t-statistic, which represents how many standard deviations away our sample slope $b$ is from the population slope $\beta$ on the sampling distribution, assuming that $\beta=0$:
     \begin{gather*}
@@
 
-    \noindent Based on the area under the curve in \textit{\autoref{fig:t_dist}} above $t=4.139$, our $p$-value is $2.916\cdot10^{-5}$.
+    \noindent Based on the area under the curve in \textit{\autoref{fig:t_dist}} above, $t=4.139$, our $p$-value is $2.916\cdot10^{-5}$.
 
@@
     The data do provide convincing evidence that the population slope $\beta$ is greater than $0$, and that there is a positive correlation between
-    parameter count and difference between train and test accuracy (train - test) in the population defined above.
+    parameter count and difference between train and test accuracy (train - test) in the population defined above. Thus, we can conclude that
+    increasing the number of parameters in the model does indeed cause overfitting.
 
@@
 
+    In our project, we aimed to determine whether increasing the parameter count of convolutional models of a specific structure caused the model to overfit,
+    or essentially memorize the train dataset and perform well on images from that set but poorly on newly introduced images. We ensured equal representation
+    of images of different classifications by randomly sampling by strata, with each strata being a group of images with the same classification.
+    By keeping the structure of the models and the dataset on which they were trained on constant, as well as randomizing the parameters of the models
+    on initialization, we prevented confounding with other variables, allowing us to establish a cause-and-effect relationship between parameter count
+    and difference between train and test accuracy (train - test). Through a $t$-test for the population slope, we found that there is a positive relationship
+    between parameter count and difference between train and test accuracy (train - test), and thus that increasing parameter count increases the difference and causes overfitting.
+
+    We could have potentially made a Type I error, because we rejected the null hypothesis. If we had made a Type I error,
+    that would mean that we found convincing evidence that increasing the parameter count of the model between 1m and 25m parameters
+    caused overfitting, when in reality it didn't. A potential consequence of this would be that we would only use models with less than 1 million parameters,
+    believing that models larger than 1 million parameters would perform worse on the test dataset, losing the potential
+    of getting better accuracy by using larger models.
+
+    However, our design included many limitations that could be addressed in future experiments.
+    We only trained models with 1m to 25m parameters, which means we can only generalize to models of these sizes.
+    In the future, we could conduct tests with a wider range of parameter sizes, which would allow us to generalize our results to a wider range of model sizes or potentially reveal a new trend with larger parameter sizes.
+
+    Another major limitation was the compute time required. Despite training relatively simple models on a small dataset, it took over two hours to train all 150 models.
+    If we wanted to scale the experiment up with more complex models or larger datasets, the compute time required could make the experiment impractical.
+    In the future, we could optimize the experiment by training the models for less epochs or using less models, although this would decrease the power of the test.
+
+    Finally, our results are only applicable to models of the specific architecture we used on a 100 image subset of the CIFAR-10 dataset, which is not useful to many people training neural networks.
+    If we wanted the test to be more useful in helping people decide the size of their models, we could perform an experiment on different model architectures and datasets, allowing a broader generalization.
+
+%    In the future, we could conduct tests beyond our current models architecture and our current parameter range,
+%    to generalize to a larger population or find different trends. It is possible that as model size increases past
+%    25 million parameters, that the difference in test and train accuracy could stop increasing and instead start decreasing.
+%    We could also conduct tests with larger training datasets and see if the slope lowers as the training dataset size increases (because overfitting generally happens on small training datasets).
+%    In the future we could also generalize our test to
+    \clearpage
+
+    \appendix
+    \section*{Appendix: Raw Data}
+    \addcontentsline{toc}{section}{Appendix: Raw Data}
+
+    \begin{longtable}{@{}
+        S[table-format=8.0]  c
+        S[table-format=8.0]  c
+        S[table-format=8.0]  c
+        @{}}
+        \caption{Raw Data: Parameter Count vs.\ Train–Test Accuracy Difference}\\
+        \toprule
+        \textbf{Param. Count} & \textbf{Accuracy}
+        & \textbf{Param. Count} & \textbf{Accuracy}
+        & \textbf{Param. Count} & \textbf{Accuracy} \\
+        \midrule
+        \endfirsthead
+
+        \toprule
+        \textbf{Param. Count} & \textbf{Accuracy}
+        & \textbf{Param. Count} & \textbf{Accuracy}
+        & \textbf{Param. Count} & \textbf{Accuracy} \\
+        \midrule
+        \endhead
+
+        \bottomrule
+        \endfoot
+
+        \num{991995}   & 0.7642 & \num{1156636} & 0.7502 & \num{1314120} & 0.7201 \\
+        \num{1481652}  & 0.7358 & \num{1653866} & 0.7463 & \num{1817930} & 0.7685 \\
+        \num{1964108}  & 0.7325 & \num{2122007} & 0.7377 & \num{2279711} & 0.7495 \\
+        \num{2443067}  & 0.7769 & \num{2612075} & 0.7425 & \num{2779778} & 0.7594 \\
+        \num{2928578}  & 0.7481 & \num{3083068} & 0.7738 & \num{3247185} & 0.7501 \\
+        \num{3409755}  & 0.7267 & \num{3574350} & 0.7405 & \num{3736748} & 0.7334 \\
+        \num{3908963}  & 0.7632 & \num{4058757} & 0.7677 & \num{4231690} & 0.7548 \\
+        \num{4387487}  & 0.7339 & \num{4537211} & 0.7427 & \num{4689447} & 0.7547 \\
+        \num{4872926}  & 0.7316 & \num{5030648} & 0.7497 & \num{5190882} & 0.7655 \\
+        \num{5353628}  & 0.7383 & \num{5518886} & 0.7448 & \num{5686656} & 0.7583 \\
+        \num{5825435}  & 0.7481 & \num{5997767} & 0.7711 & \num{6162250} & 0.7160 \\
+        \num{6304105}  & 0.7488 & \num{6472707} & 0.7484 & \num{6620711} & 0.7465 \\
+        \num{6793468}  & 0.7498 & \num{6942372} & 0.7816 & \num{7119248} & 0.7650 \\
+        \num{7274427}  & 0.7643 & \num{7455458} & 0.7449 & \num{7611411} & 0.7603 \\
+        \num{7760207}  & 0.7178 & \num{7947148} & 0.7343 & \num{8108136} & 0.7494 \\
+        \num{8261687}  & 0.7490 & \num{8413707} & 0.7760 & \num{8570111} & 0.7762 \\
+        \num{8724930}  & 0.7676 & \num{8884187} & 0.7677 & \num{9041805} & 0.7389 \\
+        \num{9203915}  & 0.7700 & \num{9364332} & 0.7457 & \num{9529295} & 0.7531 \\
+        \num{9692511}  & 0.7650 & \num{9860327} & 0.7574 & \num{10026342} & 0.7423 \\
+        \num{10183690} & 0.7185 & \num{10352393} & 0.7567 & \num{10480242} & 0.7178 \\
+        \num{10654715} & 0.7686 & \num{10813533} & 0.7413 & \num{10990748} & 0.7619 \\
+        \num{11122467} & 0.7582 & \num{11298745} & 0.7555 & \num{11465740} & 0.7503 \\
+        \num{11644706} & 0.7431 & \num{11780277} & 0.7401 & \num{11950780} & 0.7537 \\
+        \num{12133478} & 0.7462 & \num{12271857} & 0.7536 & \num{12445868} & 0.7624 \\
+        \num{12586011} & 0.7623 & \num{12773485} & 0.7606 & \num{12951004} & 0.7709 \\
+        \num{13093955} & 0.7385 & \num{13269953} & 0.7223 & \num{13399368} & 0.7681 \\
+        \num{13544767} & 0.7861 & \num{13727548} & 0.7464 & \num{13874711} & 0.7629 \\
+        \num{14055863} & 0.7519 & \num{14204772} & 0.7547 & \num{14391938} & 0.7496 \\
+        \num{14526700} & 0.7440 & \num{14678075} & 0.7440 & \num{14864381} & 0.7778 \\
+        \num{15017502} & 0.7522 & \num{15155155} & 0.8039 & \num{15348460} & 0.7520 \\
+        \num{15504047} & 0.7453 & \num{15643907} & 0.7702 & \num{15836226} & 0.7647 \\
+        \num{15977573} & 0.7830 & \num{16119548} & 0.7416 & \num{16278987} & 0.7585 \\
+        \num{16422292} & 0.7620 & \num{16623490} & 0.7814 & \num{16768300} & 0.7512 \\
+        \num{16930907} & 0.7684 & \num{17077047} & 0.7480 & \num{17277956} & 0.7671 \\
+        \num{17425583} & 0.7586 & \num{17591340} & 0.7540 & \num{17740297} & 0.7658 \\
+        \num{17889882} & 0.7834 & \num{18099850} & 0.7866 & \num{18250940} & 0.7443 \\
+        \num{18402658} & 0.7526 & \num{18572987} & 0.7770 & \num{18726035} & 0.7677 \\
+        \num{18879711} & 0.7298 & \num{19034015} & 0.7322 & \num{19246091} & 0.7612 \\
+        \num{19344507} & 0.7307 & \num{19500695} & 0.7613 & \num{19657511} & 0.7302 \\
+        \num{19814955} & 0.7481 & \num{19973027} & 0.7509 & \num{20131727} & 0.7725 \\
+        \num{20291055} & 0.7952 & \num{20451011} & 0.7881 & \num{20670818} & 0.7372 \\
+        \num{20832261} & 0.7392 & \num{20994332} & 0.7605 & \num{21157031} & 0.7665 \\
+        \num{21320358} & 0.7831 & \num{21484313} & 0.7655 & \num{21648896} & 0.7812 \\
+        \num{21814107} & 0.7388 & \num{21918875} & 0.7749 & \num{22085111} & 0.7238 \\
+        \num{22251975} & 0.7380 & \num{22419467} & 0.7686 & \num{22567754} & 0.8055 \\
+        \num{22736428} & 0.7818 & \num{22905730} & 0.7743 & \num{23008186} & 0.7285 \\
+        \num{23178495} & 0.7603 & \num{23349432} & 0.7842 & \num{23520997} & 0.7418 \\
+        \num{23693190} & 0.7992 & \num{23866011} & 0.7622 & \num{24018998} & 0.7663 \\
+        \num{24193001} & 0.7622 & \num{24367632} & 0.7711 & \num{24542891} & 0.7671 \\
+        \num{24654011} & 0.7606 & \num{24830295} & 0.7835 & \num{25007207} & 0.7820 \\
+    \end{longtable}
 \end{document}

### 2025-05-27 paper_submission.tex
made version for competition submission and fixed a few things in the paper.

--- 2025-05-27 paper_formatted.tex
@@
 
-\title{Investigating Overfitting in Convolutional Neural Networks}\date{}
+%\title{Investigating Overfitting in Convolutional Neural Networks}\date{}
 
@@
 
-    \maketitle
+    \centerline{\textbf{Investigating Overfitting in Convolutional Neural Networks}}
 
-    \section*{1. Introduction}
+    \noindent\textbf{1 Introduction}
 
-    Neural networks are a form of machine learning models, roughly inspired by how the human brain
+    Neural networks are a form of machine learning models, inspired by how the human brain
     processes information. They have become increasingly prevalent in our developing world, providing
@@
 
-    \section*{2. Statistical Question}
+    \noindent\textbf{2 Statistical Question}
 
@@
 
-    \section*{3. Data Collection}
+    \noindent\textbf{3 Data Collection}
 
@@
     on the full test set of the CIFAR-10 dataset, made up of 10,000 images. The difference between the train and test accuracy (train - test) was then
-    computed for each model and graphed on a scatter plot with the x-axis
-    as parameter count and the y-axis as the difference between train and test accuracy for each model.
+    computed for each model and graphed on a scatter plot with the $x$-axis
+    as parameter count and the $y$-axis as the difference between train and test accuracy for each model.
 
-    \section*{4. Data Display}
+    \noindent\textbf{4 Data Display}
     \begin{figure}[H]
@@
         \centering
-        \includegraphics[width=0.7\textwidth]{Images/Resid}
+        \includegraphics[width=1\textwidth]{Images/Resid}
         \caption{Residual Plot (Parameter Count vs. Residuals)}
@@
     \end{figure}
+    \noindent Because the residual plot (\textit{\autoref{fig:residuals}}) appears to have no form and because the standard
+    deviation of the residuals $S$ (\textit{from \autoref{tab:minitab}}) is small ($0.01703$), the graphical display seems to
+    indicate that the null hypothesis will be rejected.
     \begin{figure}[H]
         \centering
-        \includegraphics[width=0.7\textwidth]{Images/Resid Hist}
+        \includegraphics[width=0.6\textwidth]{Images/Resid Hist}
         \caption{Histogram of Residuals}
@@
 
-    \section*{5. Data Analysis}
+    \noindent\textbf{5 Data Analysis}
 
-    We conducted a $t$-test for the population slope $\beta$ of the least-squares regression line that relates the number of parameters in a model trained on a 100-image subset of the CIFAR-10 dataset to the difference in accuracy between training and test data (Train Accuracy $-$ Test Accuracy).
+    We conducted a $t$-test for the population slope $\beta$ of the least-squares regression line that relates the number of parameters in a model trained on a randomly selected 100-image subset of the CIFAR-10 dataset to the difference between its accuracy on training and test data (Train Accuracy $-$ Test Accuracy).
 
-    \subsection*{5.1 Condition Check}
+    \noindent\textbf{5.1 Condition Check}
 
@@
 
-    \subsection*{5.2 Calculations}
+    \noindent\textbf{5.2 Calculations}
 
-    \subsubsection*{5.2.1 Standard Error}
+    \noindent\textbf{5.2.1 Standard Error}
 
-    We used the following equation to calculate the Standard Error $SE_\beta$ of the slope $\beta$:
+    \noindent We used the following equation to calculate the Standard Error $SE_\beta$ of the slope $\beta$:
     \[
@@
 
-    \subsubsection*{5.2.2 $t$-statistic}
-    \noindent And now we can find the t-statistic, which represents how many standard deviations away our sample slope $b$ is from the population slope $\beta$ on the sampling distribution, assuming that $\beta=0$:
+    \noindent\textbf{5.2.2 $t$-statistic}
+
+    \noindent And now we can find the $t$-statistic, which represents how many standard deviations away our sample slope $b$ is from the population slope $\beta$ on the sampling distribution, assuming that $\beta=0$:
     \begin{gather*}
@@
 
-    \subsubsection*{5.2.3 $p$-value}
-    \noindent Now that we have the t-statistic, we can use it to find the $p$-value, which represents the probability of getting a test statistic
+    \noindent\textbf{5.2.3 $p$-value}
+
+    \noindent Now that we have the $t$-statistic, we can use it to find the $p$-value, which represents the probability of getting a test statistic
     of $4.139$ or higher, assuming that the population slope $\beta$ is $0$. Because we have 150 data points, we have $150 - 2 = 148$ degrees of freedom.
@@
 
-    \noindent Based on the area under the curve in \textit{\autoref{fig:t_dist}} above, $t=4.139$, our $p$-value is $2.916\cdot10^{-5}$.
+    \noindent Based on the area under the curve in \textit{\autoref{fig:t_dist}} above $t=4.139$, our $p$-value is $2.916\cdot10^{-5}$.
 
-    \section*{6. Conclusion}
+    \noindent\textbf{6 Conclusion}
 
@@
     The data do provide convincing evidence that the population slope $\beta$ is greater than $0$, and that there is a positive correlation between
-    parameter count and difference between train and test accuracy (train - test) in the population defined above. Thus, we can conclude that
+    parameter count and difference between train and test accuracy (train - test) in the population defined above. Thus, for that population, we can conclude that
     increasing the number of parameters in the model does indeed cause overfitting.
 
-    \section*{7. Reflection}
+    \noindent\textbf{7 Reflection}
 
@@
     \clearpage
-
     \appendix
@@
     \addcontentsline{toc}{section}{Appendix: Raw Data}
+
+    \begingroup
+    \scriptsize
+    \setlength{\tabcolsep}{2pt}       % tighten column separation
 
@@
         S[table-format=8.0] c
-        @{}}
+        S[table-format=8.0] c
+        S[table-format=8.0] c
+        S[table-format=8.0] c @{}}
         \caption{Raw Data: Parameter Count vs.\ Train–Test Accuracy Difference}\\
         \toprule
-        \textbf{Param. Count} & \textbf{Accuracy}
-        & \textbf{Param. Count} & \textbf{Accuracy}
-        & \textbf{Param. Count} & \textbf{Accuracy} \\
+        \textbf{Param.} & \textbf{Acc.} & \textbf{Param.} & \textbf{Acc.} &
+        \textbf{Param.} & \textbf{Acc.} & \textbf{Param.} & \textbf{Acc.} &
+        \textbf{Param.} & \textbf{Acc.} & \textbf{Param.} & \textbf{Acc.}\\
         \midrule
@@
         \toprule
-        \textbf{Param. Count} & \textbf{Accuracy}
-        & \textbf{Param. Count} & \textbf{Accuracy}
-        & \textbf{Param. Count} & \textbf{Accuracy} \\
+        \multicolumn{12}{c}{\textbf{(continued)}}\\\midrule
+        \multicolumn{2}{c}{\textbf{Col 1}} & \multicolumn{2}{c}{\textbf{Col 2}} &
+        \multicolumn{2}{c}{\textbf{Col 3}} & \multicolumn{2}{c}{\textbf{Col 4}} &
+        \multicolumn{2}{c}{\textbf{Col 5}} & \multicolumn{2}{c}{\textbf{Col 6}} \\
+        \textbf{Param.} & \textbf{Acc.} & \textbf{Param.} & \textbf{Acc.} &
+        \textbf{Param.} & \textbf{Acc.} & \textbf{Param.} & \textbf{Acc.} &
+        \textbf{Param.} & \textbf{Acc.} & \textbf{Param.} & \textbf{Acc.}\\
         \midrule
@@
 
-        \num{991995}   & 0.7642 & \num{1156636} & 0.7502 & \num{1314120} & 0.7201 \\
-        \num{1481652}  & 0.7358 & \num{1653866} & 0.7463 & \num{1817930} & 0.7685 \\
-        \num{1964108}  & 0.7325 & \num{2122007} & 0.7377 & \num{2279711} & 0.7495 \\
-        \num{2443067}  & 0.7769 & \num{2612075} & 0.7425 & \num{2779778} & 0.7594 \\
-        \num{2928578}  & 0.7481 & \num{3083068} & 0.7738 & \num{3247185} & 0.7501 \\
-        \num{3409755}  & 0.7267 & \num{3574350} & 0.7405 & \num{3736748} & 0.7334 \\
-        \num{3908963}  & 0.7632 & \num{4058757} & 0.7677 & \num{4231690} & 0.7548 \\
-        \num{4387487}  & 0.7339 & \num{4537211} & 0.7427 & \num{4689447} & 0.7547 \\
-        \num{4872926}  & 0.7316 & \num{5030648} & 0.7497 & \num{5190882} & 0.7655 \\
-        \num{5353628}  & 0.7383 & \num{5518886} & 0.7448 & \num{5686656} & 0.7583 \\
-        \num{5825435}  & 0.7481 & \num{5997767} & 0.7711 & \num{6162250} & 0.7160 \\
-        \num{6304105}  & 0.7488 & \num{6472707} & 0.7484 & \num{6620711} & 0.7465 \\
-        \num{6793468}  & 0.7498 & \num{6942372} & 0.7816 & \num{7119248} & 0.7650 \\
-        \num{7274427}  & 0.7643 & \num{7455458} & 0.7449 & \num{7611411} & 0.7603 \\
-        \num{7760207}  & 0.7178 & \num{7947148} & 0.7343 & \num{8108136} & 0.7494 \\
-        \num{8261687}  & 0.7490 & \num{8413707} & 0.7760 & \num{8570111} & 0.7762 \\
-        \num{8724930}  & 0.7676 & \num{8884187} & 0.7677 & \num{9041805} & 0.7389 \\
-        \num{9203915}  & 0.7700 & \num{9364332} & 0.7457 & \num{9529295} & 0.7531 \\
-        \num{9692511}  & 0.7650 & \num{9860327} & 0.7574 & \num{10026342} & 0.7423 \\
-        \num{10183690} & 0.7185 & \num{10352393} & 0.7567 & \num{10480242} & 0.7178 \\
-        \num{10654715} & 0.7686 & \num{10813533} & 0.7413 & \num{10990748} & 0.7619 \\
-        \num{11122467} & 0.7582 & \num{11298745} & 0.7555 & \num{11465740} & 0.7503 \\
-        \num{11644706} & 0.7431 & \num{11780277} & 0.7401 & \num{11950780} & 0.7537 \\
-        \num{12133478} & 0.7462 & \num{12271857} & 0.7536 & \num{12445868} & 0.7624 \\
-        \num{12586011} & 0.7623 & \num{12773485} & 0.7606 & \num{12951004} & 0.7709 \\
-        \num{13093955} & 0.7385 & \num{13269953} & 0.7223 & \num{13399368} & 0.7681 \\
-        \num{13544767} & 0.7861 & \num{13727548} & 0.7464 & \num{13874711} & 0.7629 \\
-        \num{14055863} & 0.7519 & \num{14204772} & 0.7547 & \num{14391938} & 0.7496 \\
-        \num{14526700} & 0.7440 & \num{14678075} & 0.7440 & \num{14864381} & 0.7778 \\
-        \num{15017502} & 0.7522 & \num{15155155} & 0.8039 & \num{15348460} & 0.7520 \\
-        \num{15504047} & 0.7453 & \num{15643907} & 0.7702 & \num{15836226} & 0.7647 \\
-        \num{15977573} & 0.7830 & \num{16119548} & 0.7416 & \num{16278987} & 0.7585 \\
-        \num{16422292} & 0.7620 & \num{16623490} & 0.7814 & \num{16768300} & 0.7512 \\
-        \num{16930907} & 0.7684 & \num{17077047} & 0.7480 & \num{17277956} & 0.7671 \\
-        \num{17425583} & 0.7586 & \num{17591340} & 0.7540 & \num{17740297} & 0.7658 \\
-        \num{17889882} & 0.7834 & \num{18099850} & 0.7866 & \num{18250940} & 0.7443 \\
-        \num{18402658} & 0.7526 & \num{18572987} & 0.7770 & \num{18726035} & 0.7677 \\
-        \num{18879711} & 0.7298 & \num{19034015} & 0.7322 & \num{19246091} & 0.7612 \\
-        \num{19344507} & 0.7307 & \num{19500695} & 0.7613 & \num{19657511} & 0.7302 \\
-        \num{19814955} & 0.7481 & \num{19973027} & 0.7509 & \num{20131727} & 0.7725 \\
-        \num{20291055} & 0.7952 & \num{20451011} & 0.7881 & \num{20670818} & 0.7372 \\
-        \num{20832261} & 0.7392 & \num{20994332} & 0.7605 & \num{21157031} & 0.7665 \\
-        \num{21320358} & 0.7831 & \num{21484313} & 0.7655 & \num{21648896} & 0.7812 \\
-        \num{21814107} & 0.7388 & \num{21918875} & 0.7749 & \num{22085111} & 0.7238 \\
-        \num{22251975} & 0.7380 & \num{22419467} & 0.7686 & \num{22567754} & 0.8055 \\
-        \num{22736428} & 0.7818 & \num{22905730} & 0.7743 & \num{23008186} & 0.7285 \\
-        \num{23178495} & 0.7603 & \num{23349432} & 0.7842 & \num{23520997} & 0.7418 \\
-        \num{23693190} & 0.7992 & \num{23866011} & 0.7622 & \num{24018998} & 0.7663 \\
-        \num{24193001} & 0.7622 & \num{24367632} & 0.7711 & \num{24542891} & 0.7671 \\
-        \num{24654011} & 0.7606 & \num{24830295} & 0.7835 & \num{25007207} & 0.7820 \\
+        \num{991995}&0.7642  & \num{1156636}&0.7502  & \num{1314120}&0.7201  &
+        \num{1481652}&0.7358  & \num{1653866}&0.7463  & \num{1817930}&0.7685  \\
+        \num{1964108}&0.7325  & \num{2122007}&0.7377  & \num{2279711}&0.7495  &
+        \num{2443067}&0.7769  & \num{2612075}&0.7425  & \num{2779778}&0.7594  \\
+        \num{2928578}&0.7481  & \num{3083068}&0.7738  & \num{3247185}&0.7501  &
+        \num{3409755}&0.7267  & \num{3574350}&0.7405  & \num{3736748}&0.7334  \\
+        \num{3908963}&0.7632  & \num{4058757}&0.7677  & \num{4231690}&0.7548  &
+        \num{4387487}&0.7339  & \num{4537211}&0.7427  & \num{4689447}&0.7547  \\
+        \num{4872926}&0.7316  & \num{5030648}&0.7497  & \num{5190882}&0.7655  &
+        \num{5353628}&0.7383  & \num{5518886}&0.7448  & \num{5686656}&0.7583  \\
+        \num{5825435}&0.7481  & \num{5997767}&0.7711  & \num{6162250}&0.7160  &
+        \num{6304105}&0.7488  & \num{6472707}&0.7484  & \num{6620711}&0.7465  \\
+        \num{6793468}&0.7498  & \num{6942372}&0.7816  & \num{7119248}&0.7650  &
+        \num{7274427}&0.7643  & \num{7455458}&0.7449  & \num{7611411}&0.7603  \\
+        \num{7760207}&0.7178  & \num{7947148}&0.7343  & \num{8108136}&0.7494  &
+        \num{8261687}&0.7490  & \num{8413707}&0.7760  & \num{8570111}&0.7762  \\
+        \num{8724930}&0.7676  & \num{8884187}&0.7677  & \num{9041805}&0.7389  &
+        \num{9203915}&0.7700  & \num{9364332}&0.7457  & \num{9529295}&0.7531  \\
+        \num{9692511}&0.7650  & \num{9860327}&0.7574  & \num{10026342}&0.7423 &
+        \num{10183690}&0.7185 & \num{10352393}&0.7567 & \num{10480242}&0.7178 \\
+        \num{10654715}&0.7686 & \num{10813533}&0.7413 & \num{10990748}&0.7619 &
+        \num{11122467}&0.7582 & \num{11298745}&0.7555 & \num{11465740}&0.7503 \\
+        \num{11644706}&0.7431 & \num{11780277}&0.7401 & \num{11950780}&0.7537 &
+        \num{12133478}&0.7462 & \num{12271857}&0.7536 & \num{12445868}&0.7624 \\
+        \num{12586011}&0.7623 & \num{12773485}&0.7606 & \num{12951004}&0.7709 &
+        \num{13093955}&0.7385 & \num{13269953}&0.7223 & \num{13399368}&0.7681 \\
+        \num{13544767}&0.7861 & \num{13727548}&0.7464 & \num{13874711}&0.7629 &
+        \num{14055863}&0.7519 & \num{14204772}&0.7547 & \num{14391938}&0.7496 \\
+        \num{14526700}&0.7440 & \num{14678075}&0.7440 & \num{14864381}&0.7778 &
+        \num{15017502}&0.7522 & \num{15155155}&0.8039 & \num{15348460}&0.7520 \\
+        \num{15504047}&0.7453 & \num{15643907}&0.7702 & \num{15836226}&0.7647 &
+        \num{15977573}&0.7830 & \num{16119548}&0.7416 & \num{16278987}&0.7585 \\
+        \num{16422292}&0.7620 & \num{16623490}&0.7814 & \num{16768300}&0.7512 &
+        \num{16930907}&0.7684 & \num{17077047}&0.7480 & \num{17277956}&0.7671 \\
+        \num{17425583}&0.7586 & \num{17591340}&0.7540 & \num{17740297}&0.7658 &
+        \num{17889882}&0.7834 & \num{18099850}&0.7866 & \num{18250940}&0.7443 \\
+        \num{18402658}&0.7526 & \num{18572987}&0.7770 & \num{18726035}&0.7677 &
+        \num{18879711}&0.7298 & \num{19034015}&0.7322 & \num{19246091}&0.7612 \\
+        \num{19344507}&0.7307 & \num{19500695}&0.7613 & \num{19657511}&0.7302 &
+        \num{19814955}&0.7481 & \num{19973027}&0.7509 & \num{20131727}&0.7725 \\
+        \num{20291055}&0.7952 & \num{20451011}&0.7881 & \num{20670818}&0.7372 &
+        \num{20832261}&0.7392 & \num{20994332}&0.7605 & \num{21157031}&0.7665 \\
+        \num{21320358}&0.7831 & \num{21484313}&0.7655 & \num{21648896}&0.7812 &
+        \num{21814107}&0.7388 & \num{21918875}&0.7749 & \num{22085111}&0.7238 \\
+        \num{22251975}&0.7380 & \num{22419467}&0.7686 & \num{22567754}&0.8055 &
+        \num{22736428}&0.7818 & \num{22905730}&0.7743 & \num{23008186}&0.7285 \\
+        \num{23178495}&0.7603 & \num{23349432}&0.7842 & \num{23520997}&0.7418 &
+        \num{23693190}&0.7992 & \num{23866011}&0.7622 & \num{24018998}&0.7663 \\
+        \num{24193001}&0.7622 & \num{24367632}&0.7711 & \num{24542891}&0.7671 &
+        \num{24654011}&0.7606 & \num{24830295}&0.7835 & \num{25007207}&0.7820 \\
     \end{longtable}
+    \endgroup
+
 \end{document}

### 2025-05-27 paper_formatted.tex
push to fix brier's version

@@
 %! Author = JustinMa
-%! Date = 5/22/25
+%! Date = 5/27/25
 
@@
 
-    \section*{1. Introduction}
+    \section*{1 Introduction}
 
-    Neural networks are a form of machine learning models, roughly inspired by how the human brain
+    Neural networks are a form of machine learning models, inspired by how the human brain
     processes information. They have become increasingly prevalent in our developing world, providing
@@
 
-    \section*{2. Statistical Question}
+    \section*{2 Statistical Question}
 
@@
 
-    \section*{3. Data Collection}
+    \section*{3 Data Collection}
 
@@
     on the full test set of the CIFAR-10 dataset, made up of 10,000 images. The difference between the train and test accuracy (train - test) was then
-    computed for each model and graphed on a scatter plot with the x-axis
-    as parameter count and the y-axis as the difference between train and test accuracy for each model.
+    computed for each model and graphed on a scatter plot with the $x$-axis
+    as parameter count and the $y$-axis as the difference between train and test accuracy for each model.
 
-    \section*{4. Data Display}
+    \section*{4 Data Display}
     \begin{figure}[H]
@@
         \centering
-        \includegraphics[width=0.7\textwidth]{Images/Resid}
+        \includegraphics[width=0.6\textwidth]{Images/Resid}
         \caption{Residual Plot (Parameter Count vs. Residuals)}
@@
 
-    \section*{5. Data Analysis}
+    \section*{5 Data Analysis}
 
-    We conducted a $t$-test for the population slope $\beta$ of the least-squares regression line that relates the number of parameters in a model trained on a 100-image subset of the CIFAR-10 dataset to the difference in accuracy between training and test data (Train Accuracy $-$ Test Accuracy).
+    We conducted a $t$-test for the population slope $\beta$ of the least-squares regression line that relates the number of parameters in a model trained on a randomly selected 100-image subset of the CIFAR-10 dataset to the difference between its accuracy on training and test data (Train Accuracy $-$ Test Accuracy).
 
@@
     \subsubsection*{5.2.2 $t$-statistic}
-    \noindent And now we can find the t-statistic, which represents how many standard deviations away our sample slope $b$ is from the population slope $\beta$ on the sampling distribution, assuming that $\beta=0$:
+    \noindent And now we can find the $t$-statistic, which represents how many standard deviations away our sample slope $b$ is from the population slope $\beta$ on the sampling distribution, assuming that $\beta=0$:
     \begin{gather*}
@@
     \subsubsection*{5.2.3 $p$-value}
-    \noindent Now that we have the t-statistic, we can use it to find the $p$-value, which represents the probability of getting a test statistic
+    \noindent Now that we have the $t$-statistic, we can use it to find the $p$-value, which represents the probability of getting a test statistic
     of $4.139$ or higher, assuming that the population slope $\beta$ is $0$. Because we have 150 data points, we have $150 - 2 = 148$ degrees of freedom.
@@
 
-    \noindent Based on the area under the curve in \textit{\autoref{fig:t_dist}} above, $t=4.139$, our $p$-value is $2.916\cdot10^{-5}$.
+    \noindent Based on the area under the curve in \textit{\autoref{fig:t_dist}} above $t=4.139$, our $p$-value is $2.916\cdot10^{-5}$.
 
-    \section*{6. Conclusion}
+    \section*{6 Conclusion}
 
@@
     The data do provide convincing evidence that the population slope $\beta$ is greater than $0$, and that there is a positive correlation between
-    parameter count and difference between train and test accuracy (train - test) in the population defined above. Thus, we can conclude that
+    parameter count and difference between train and test accuracy (train - test) in the population defined above. Thus, for that population, we can conclude that
     increasing the number of parameters in the model does indeed cause overfitting.
 
-    \section*{7. Reflection}
+    \section*{7 Reflection}
 

### 2025-05-27 paper_formatted.tex
fix to reflection formatting in formatted paper.

@@
 
-    We could have potentially made a Type I error, because we rejected the null hypothesis. If we had made a Type I error,
+    \bigskip\noindent We could have potentially made a Type I error, because we rejected the null hypothesis. If we had made a Type I error,
     that would mean that we found convincing evidence that increasing the parameter count of the model between 1m and 25m parameters
@@
 
-    However, our design included many limitations that could be addressed in future experiments.
+    \bigskip\noindent However, our design included many limitations that could be addressed in future experiments.
     We only trained models with 1m to 25m parameters, which means we can only generalize to models of these sizes.
@@
 
-    Another major limitation was the compute time required. Despite training relatively simple models on a small dataset, it took over two hours to train all 150 models.
+    \bigskip\noindent Another major limitation was the compute time required. Despite training relatively simple models on a small dataset, it took over two hours to train all 150 models.
     If we wanted to scale the experiment up with more complex models or larger datasets, the compute time required could make the experiment impractical.
@@
 
-    Finally, our results are only applicable to models of the specific architecture we used on a 100 image subset of the CIFAR-10 dataset, which is not useful to many people training neural networks.
+    \bigskip\noindent Finally, our results are only applicable to models of the specific architecture we used on a 100 image subset of the CIFAR-10 dataset, which is not useful to many people training neural networks.
     If we wanted the test to be more useful in helping people decide the size of their models, we could perform an experiment on different model architectures and datasets, allowing a broader generalization.
@@
     \clearpage
+    \appendix
+    \textbf{Appendix: Raw Data}
+    \addcontentsline{toc}{section}{Appendix: Raw Data}
 
-    \appendix
-    \section*{Appendix: Raw Data}
-    \addcontentsline{toc}{section}{Appendix: Raw Data}
+    \begingroup
+    \scriptsize
+    \setlength{\tabcolsep}{2pt}       % tighten column separation
 
@@
 
-        \num{991995}   & 0.7642 & \num{1156636} & 0.7502 & \num{1314120} & 0.7201 \\
-        \num{1481652}  & 0.7358 & \num{1653866} & 0.7463 & \num{1817930} & 0.7685 \\
-        \num{1964108}  & 0.7325 & \num{2122007} & 0.7377 & \num{2279711} & 0.7495 \\
-        \num{2443067}  & 0.7769 & \num{2612075} & 0.7425 & \num{2779778} & 0.7594 \\
-        \num{2928578}  & 0.7481 & \num{3083068} & 0.7738 & \num{3247185} & 0.7501 \\
-        \num{3409755}  & 0.7267 & \num{3574350} & 0.7405 & \num{3736748} & 0.7334 \\
-        \num{3908963}  & 0.7632 & \num{4058757} & 0.7677 & \num{4231690} & 0.7548 \\
-        \num{4387487}  & 0.7339 & \num{4537211} & 0.7427 & \num{4689447} & 0.7547 \\
-        \num{4872926}  & 0.7316 & \num{5030648} & 0.7497 & \num{5190882} & 0.7655 \\
-        \num{5353628}  & 0.7383 & \num{5518886} & 0.7448 & \num{5686656} & 0.7583 \\
-        \num{5825435}  & 0.7481 & \num{5997767} & 0.7711 & \num{6162250} & 0.7160 \\
-        \num{6304105}  & 0.7488 & \num{6472707} & 0.7484 & \num{6620711} & 0.7465 \\
-        \num{6793468}  & 0.7498 & \num{6942372} & 0.7816 & \num{7119248} & 0.7650 \\
-        \num{7274427}  & 0.7643 & \num{7455458} & 0.7449 & \num{7611411} & 0.7603 \\
-        \num{7760207}  & 0.7178 & \num{7947148} & 0.7343 & \num{8108136} & 0.7494 \\
-        \num{8261687}  & 0.7490 & \num{8413707} & 0.7760 & \num{8570111} & 0.7762 \\
-        \num{8724930}  & 0.7676 & \num{8884187} & 0.7677 & \num{9041805} & 0.7389 \\
-        \num{9203915}  & 0.7700 & \num{9364332} & 0.7457 & \num{9529295} & 0.7531 \\
-        \num{9692511}  & 0.7650 & \num{9860327} & 0.7574 & \num{10026342} & 0.7423 \\
-        \num{10183690} & 0.7185 & \num{10352393} & 0.7567 & \num{10480242} & 0.7178 \\
-        \num{10654715} & 0.7686 & \num{10813533} & 0.7413 & \num{10990748} & 0.7619 \\
-        \num{11122467} & 0.7582 & \num{11298745} & 0.7555 & \num{11465740} & 0.7503 \\
-        \num{11644706} & 0.7431 & \num{11780277} & 0.7401 & \num{11950780} & 0.7537 \\
-        \num{12133478} & 0.7462 & \num{12271857} & 0.7536 & \num{12445868} & 0.7624 \\
-        \num{12586011} & 0.7623 & \num{12773485} & 0.7606 & \num{12951004} & 0.7709 \\
-        \num{13093955} & 0.7385 & \num{13269953} & 0.7223 & \num{13399368} & 0.7681 \\
-        \num{13544767} & 0.7861 & \num{13727548} & 0.7464 & \num{13874711} & 0.7629 \\
-        \num{14055863} & 0.7519 & \num{14204772} & 0.7547 & \num{14391938} & 0.7496 \\
-        \num{14526700} & 0.7440 & \num{14678075} & 0.7440 & \num{14864381} & 0.7778 \\
-        \num{15017502} & 0.7522 & \num{15155155} & 0.8039 & \num{15348460} & 0.7520 \\
-        \num{15504047} & 0.7453 & \num{15643907} & 0.7702 & \num{15836226} & 0.7647 \\
-        \num{15977573} & 0.7830 & \num{16119548} & 0.7416 & \num{16278987} & 0.7585 \\
-        \num{16422292} & 0.7620 & \num{16623490} & 0.7814 & \num{16768300} & 0.7512 \\
-        \num{16930907} & 0.7684 & \num{17077047} & 0.7480 & \num{17277956} & 0.7671 \\
-        \num{17425583} & 0.7586 & \num{17591340} & 0.7540 & \num{17740297} & 0.7658 \\
-        \num{17889882} & 0.7834 & \num{18099850} & 0.7866 & \num{18250940} & 0.7443 \\
-        \num{18402658} & 0.7526 & \num{18572987} & 0.7770 & \num{18726035} & 0.7677 \\
-        \num{18879711} & 0.7298 & \num{19034015} & 0.7322 & \num{19246091} & 0.7612 \\
-        \num{19344507} & 0.7307 & \num{19500695} & 0.7613 & \num{19657511} & 0.7302 \\
-        \num{19814955} & 0.7481 & \num{19973027} & 0.7509 & \num{20131727} & 0.7725 \\
-        \num{20291055} & 0.7952 & \num{20451011} & 0.7881 & \num{20670818} & 0.7372 \\
-        \num{20832261} & 0.7392 & \num{20994332} & 0.7605 & \num{21157031} & 0.7665 \\
-        \num{21320358} & 0.7831 & \num{21484313} & 0.7655 & \num{21648896} & 0.7812 \\
-        \num{21814107} & 0.7388 & \num{21918875} & 0.7749 & \num{22085111} & 0.7238 \\
-        \num{22251975} & 0.7380 & \num{22419467} & 0.7686 & \num{22567754} & 0.8055 \\
-        \num{22736428} & 0.7818 & \num{22905730} & 0.7743 & \num{23008186} & 0.7285 \\
-        \num{23178495} & 0.7603 & \num{23349432} & 0.7842 & \num{23520997} & 0.7418 \\
-        \num{23693190} & 0.7992 & \num{23866011} & 0.7622 & \num{24018998} & 0.7663 \\
-        \num{24193001} & 0.7622 & \num{24367632} & 0.7711 & \num{24542891} & 0.7671 \\
-        \num{24654011} & 0.7606 & \num{24830295} & 0.7835 & \num{25007207} & 0.7820 \\
+        \num{991995}&0.7642  & \num{1156636}&0.7502  & \num{1314120}&0.7201  &
+        \num{1481652}&0.7358  & \num{1653866}&0.7463  & \num{1817930}&0.7685  \\
+        \num{1964108}&0.7325  & \num{2122007}&0.7377  & \num{2279711}&0.7495  &
+        \num{2443067}&0.7769  & \num{2612075}&0.7425  & \num{2779778}&0.7594  \\
+        \num{2928578}&0.7481  & \num{3083068}&0.7738  & \num{3247185}&0.7501  &
+        \num{3409755}&0.7267  & \num{3574350}&0.7405  & \num{3736748}&0.7334  \\
+        \num{3908963}&0.7632  & \num{4058757}&0.7677  & \num{4231690}&0.7548  &
+        \num{4387487}&0.7339  & \num{4537211}&0.7427  & \num{4689447}&0.7547  \\
+        \num{4872926}&0.7316  & \num{5030648}&0.7497  & \num{5190882}&0.7655  &
+        \num{5353628}&0.7383  & \num{5518886}&0.7448  & \num{5686656}&0.7583  \\
+        \num{5825435}&0.7481  & \num{5997767}&0.7711  & \num{6162250}&0.7160  &
+        \num{6304105}&0.7488  & \num{6472707}&0.7484  & \num{6620711}&0.7465  \\
+        \num{6793468}&0.7498  & \num{6942372}&0.7816  & \num{7119248}&0.7650  &
+        \num{7274427}&0.7643  & \num{7455458}&0.7449  & \num{7611411}&0.7603  \\
+        \num{7760207}&0.7178  & \num{7947148}&0.7343  & \num{8108136}&0.7494  &
+        \num{8261687}&0.7490  & \num{8413707}&0.7760  & \num{8570111}&0.7762  \\
+        \num{8724930}&0.7676  & \num{8884187}&0.7677  & \num{9041805}&0.7389  &
+        \num{9203915}&0.7700  & \num{9364332}&0.7457  & \num{9529295}&0.7531  \\
+        \num{9692511}&0.7650  & \num{9860327}&0.7574  & \num{10026342}&0.7423 &
+        \num{10183690}&0.7185 & \num{10352393}&0.7567 & \num{10480242}&0.7178 \\
+        \num{10654715}&0.7686 & \num{10813533}&0.7413 & \num{10990748}&0.7619 &
+        \num{11122467}&0.7582 & \num{11298745}&0.7555 & \num{11465740}&0.7503 \\
+        \num{11644706}&0.7431 & \num{11780277}&0.7401 & \num{11950780}&0.7537 &
+        \num{12133478}&0.7462 & \num{12271857}&0.7536 & \num{12445868}&0.7624 \\
+        \num{12586011}&0.7623 & \num{12773485}&0.7606 & \num{12951004}&0.7709 &
+        \num{13093955}&0.7385 & \num{13269953}&0.7223 & \num{13399368}&0.7681 \\
+        \num{13544767}&0.7861 & \num{13727548}&0.7464 & \num{13874711}&0.7629 &
+        \num{14055863}&0.7519 & \num{14204772}&0.7547 & \num{14391938}&0.7496 \\
+        \num{14526700}&0.7440 & \num{14678075}&0.7440 & \num{14864381}&0.7778 &
+        \num{15017502}&0.7522 & \num{15155155}&0.8039 & \num{15348460}&0.7520 \\
+        \num{15504047}&0.7453 & \num{15643907}&0.7702 & \num{15836226}&0.7647 &
+        \num{15977573}&0.7830 & \num{16119548}&0.7416 & \num{16278987}&0.7585 \\
+        \num{16422292}&0.7620 & \num{16623490}&0.7814 & \num{16768300}&0.7512 &
+        \num{16930907}&0.7684 & \num{17077047}&0.7480 & \num{17277956}&0.7671 \\
+        \num{17425583}&0.7586 & \num{17591340}&0.7540 & \num{17740297}&0.7658 &
+        \num{17889882}&0.7834 & \num{18099850}&0.7866 & \num{18250940}&0.7443 \\
+        \num{18402658}&0.7526 & \num{18572987}&0.7770 & \num{18726035}&0.7677 &
+        \num{18879711}&0.7298 & \num{19034015}&0.7322 & \num{19246091}&0.7612 \\
+        \num{19344507}&0.7307 & \num{19500695}&0.7613 & \num{19657511}&0.7302 &
+        \num{19814955}&0.7481 & \num{19973027}&0.7509 & \num{20131727}&0.7725 \\
+        \num{20291055}&0.7952 & \num{20451011}&0.7881 & \num{20670818}&0.7372 &
+        \num{20832261}&0.7392 & \num{20994332}&0.7605 & \num{21157031}&0.7665 \\
+        \num{21320358}&0.7831 & \num{21484313}&0.7655 & \num{21648896}&0.7812 &
+        \num{21814107}&0.7388 & \num{21918875}&0.7749 & \num{22085111}&0.7238 \\
+        \num{22251975}&0.7380 & \num{22419467}&0.7686 & \num{22567754}&0.8055 &
+        \num{22736428}&0.7818 & \num{22905730}&0.7743 & \num{23008186}&0.7285 \\
+        \num{23178495}&0.7603 & \num{23349432}&0.7842 & \num{23520997}&0.7418 &
+        \num{23693190}&0.7992 & \num{23866011}&0.7622 & \num{24018998}&0.7663 \\
+        \num{24193001}&0.7622 & \num{24367632}&0.7711 & \num{24542891}&0.7671 &
+        \num{24654011}&0.7606 & \num{24830295}&0.7835 & \num{25007207}&0.7820 \\
     \end{longtable}
+    \endgroup
 \end{document}
